Contracts for Contracts

### 2023-06-26 paper/formal_model.tex
WIP
update grammar in paper
update syntax

the core model of the language $\lambda_\lang$
\todo{there must be some interesting points/trade-offs about the design}

@@

\subsection{Semantics}

@@

dynamic semantics

\subsection{Compilation of Specification}

>>>>

To articulate our approach and \lang's semantics, we present a core model
smart contract language $\lambda_\lang$ equipped with
behavioral contracts. The language modulo behavioral
contracts is entirely a subset of Solidity.
This section presents $\lambda_\lang$'s abstract syntax, static semantics, and
translation semantics.

@@

\Cref{fig:syntax} shows the abtract syntax of $\lambda_\lang$.

\subsection{Static Semantics}

@@

dynamic semantics
\yy{do we want to model the context of contracts? (instead of reasoning one contract)}

The semantics of contracts

\subsection{Translation Semantics}
